% import packages
\documentclass[12pt,a4paper]{article}
%\usepackage{times}
%\usepackage{wrapfig}
%\usepackage{latexsym}
%\usepackage{subcaption}
%\usepackage{csquotes}
%\usepackage{placeins}
%\usepackage{cleveref}
%\usepackage{setspace}
%\onehalfspacing
%\usepackage{array}
\usepackage{graphicx}
\usepackage{calc}
\usepackage{soul}
\usepackage[dvipsnames]{xcolor}
\usepackage[titles]{tocloft}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{threeparttable}
\usepackage{enumitem}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{ragged2e}
\usepackage[hidelinks]{hyperref}
\usepackage[font=footnotesize]{caption}
\usepackage{csquotes}
\usepackage{float}
\usepackage[round,sort]{natbib}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,decorations.pathreplacing,shapes,calc,fit}
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{url}
\usepackage{array,tabularx}
\usepackage{calc}

% define global variables
\newlength{\bibitemsep}\setlength{\bibitemsep}{.2\baselineskip plus .05\baselineskip minus .05\baselineskip}
\newlength{\bibparskip}\setlength{\bibparskip}{3pt}
\let\oldthebibliography\thebibliography
\renewcommand\thebibliography[1]{%
  \oldthebibliography{#1}%
  \setlength{\parskip}{\bibitemsep}%
  \setlength{\itemsep}{\bibparskip}%
}
\newlength{\DepthReference}
\settodepth{\DepthReference}{g}%relative to a depth of a letter.
\newlength{\HeightReference}
\settoheight{\HeightReference}{T}
\newlength{\Width}%
\newcommand{\MyColorBox}[2][red]%
{%
    \settowidth{\Width}{#2}%
    %\setlength{\fboxsep}{0pt}%
    \colorbox{#1}%
    {%      
        \raisebox{-\DepthReference}%
        {%
                \parbox[b][\HeightReference+\DepthReference][c]{\Width}{\centering#2}%
        }%
    }%
}
\setlength{\fboxsep}{1pt}
\setlength{\cftbeforesecskip}{1ex}
\colorlet{LightForestGreen}{ForestGreen!50!}
\colorlet{LightCyan}{Cyan!30!}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\captionsetup[algorithm]{labelsep=colon}
\algnewcommand\algorithmicforeach{\textbf{for each}}
\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}
\geometry{top=2.5cm,
		bottom=2.5cm}
\graphicspath{{img/}}
\newcommand\BibTeX{B\textsc{ib}\TeX}
%\renewcommand{\contentsname}{Table of Contents}
%\renewcommand{\refname}{Bibliography}
\newcolumntype{L}[1]{>{\RaggedRight\hspace{0pt}}p{#1}}
\newcolumntype{R}[1]{>{\RaggedLeft\hspace{0pt}}p{#1}}
\captionsetup[figure]{font=footnotesize,labelfont=footnotesize,labelfont={bf},labelformat={default},labelsep=period,name={Fig.}, justification=centering,singlelinecheck=false, width = \linewidth}
\captionsetup[table]{font=footnotesize,labelfont=footnotesize,labelfont={bf},labelformat={default},labelsep=period,name={Table},justification=centering, singlelinecheck=false, width = \linewidth}

% define admin variables
\title{Sentiment Analysis and Argumentation Mining in United
Nations Security Council Speeches}
\author{Juliane Hanel, Atreya Shankar\\
\texttt{\{hanel,shankar\}@uni-potsdam.de} \\
PM: Mining Sentiments and Arguments, WiSe 2019/20 \\
Prof. Dr. Manfred Stede \\
Applied Computational Linguistics\\
University of Potsdam}
\date{\today}

\begin{document}
\newgeometry{}
\maketitle
\thispagestyle{empty}
\begin{abstract}
The United Nations Security Council (UNSC) corpus from \citet{schnfeld2019security} is a novel political speech corpus containing $\sim$65,000 textual speech records from $\sim$5,000 security council meetings over the years of 1995-2017. Due to its large size and wide temporal distribution, it could be a very useful corpus for various Natural Language Processing (NLP) tasks in the political domain. One limitation of the current version of this corpus is its lack of extensive handwritten annotations; which diminish its utility for downstream supervised NLP tasks. In order to address this limitation, our project aims to evaluate and provide machine-driven sentiment and argumentation annotations for this corpus. We utilize state-of-the-art sentiment analysis and argumentation mining tools for this purpose, which include \texttt{VADER}, \texttt{AFINN}, and \texttt{TextBlob} for sentiment analysis and a political-domain fine-tuned version of the \texttt{ALBERT} language model for argumentation mining. Our automatic annotations, while not being as reliable as human annotations, nevertheless provide an initial foothold for future human annotations to follow-through.
\end{abstract}
\newpage
\restoregeometry
\thispagestyle{empty}
\tableofcontents
\newpage
\setcounter{page}{1}
\thispagestyle{plain}
\input{section_1}
\input{section_2}
\input{section_3}
\input{section_4}
\input{section_5}
\input{section_6}
\newpage
\addcontentsline{toc}{section}{References}
\bibliography{bibtex}
\bibliographystyle{apalike}
\nocite{*}
\end{document}